Matching Bullets

### 2015-12-09 imaging-paper.Rnw
Rewrite the end of the intro + beginning of methodology

\section{Problem Statement}
\eh{XXX do we still need this section?}

\section{Methodology}
Throughout this section, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study \cite{hamby:2009}. Ten consecutively rifled Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison.

@@

3D topographical images of each bullet were taken using a NanoFocus lens at 20x magnification and made publicly available on the NIST Ballistics Database Project\footnote{\url{http://www.nist.gov/forensics/ballisticsdb/hamby-consecutively-rifled-barrels.cfm}} in a format called x3p (XML 3-D Surface Profile). 
x3p is a container format conforming to the ISO5436-2 standard\footnote{\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}}, implemented to provide a simple and standard conforming way to exchange 2D and 3D profile data. 
%The x3p format was developed as a means for forensic examiners to easily exchange images in a standard format. 
x3p was adopted by the OpenFMC (Open Forensic Metrology Consortium\footnote{\url{http://www.openfmc.org/}}), a group of academic, industry, and government Firearm Forensics researchers whose aim is to establish best practices for researchers using metrology in the forensic sciences.

@@

The primary goal in this type of forensic analysis is to identify markings in an attempt to match two bullets. Gun barrels should produce similar markings on bullets fired consecutively, and the careful analysis of these surface images can help us determine whether two bullets are a match. However, this process has traditionally required forensic experts to perform the analysis, also required physical examination of the bullets. We've produced a framework which, in software, allows for the analysis of the surface topologies, and also transcribes the markings into a 2D plotting framework which we believe makes identification of matches easier for the lay person.

>>>>

@@

The primary goal in this type of forensic analysis is to identify markings in an attempt to match two bullets. Since gun barrels should produce similar markings on bullets fired consecutively, the careful analysis of these surface images can help us determine whether two bullets are a match. However, this process has traditionally required forensic experts to perform the analysis, and required physical examination of the bullets. We've produced a framework which, in software, allows for the analysis of the surface topologies, and the transcription of the markings into a 2D plotting framework which we believe makes identification of matches easier for the lay person.

\section{Methodology}
Throughout this paper, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study \cite{hamby:2009}. Ten consecutively rifled Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison.

3D topographical images of each bullet were taken using a NanoFocus lens at 20x magnification and made publicly available on the NIST Ballistics Database Project\footnote{\url{http://www.nist.gov/forensics/ballisticsdb/hamby-consecutively-rifled-barrels.cfm}} in a format called x3p (XML 3-D Surface Profile). x3p is a container format conforming to the ISO5436-2 standard\footnote{\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}}, implemented to provide a simple and standard conforming way to exchange 2D and 3D profile data. x3p was adopted by the OpenFMC (Open Forensic Metrology Consortium\footnote{\url{http://www.openfmc.org/}}), a group of academic, industry, and government Firearm Forensics researchers whose aim is to establish best practices for researchers using metrology in the forensic sciences.

@@
